\documentclass[letterpaper,11pt]{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.25in]{geometry}

\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries\theauthor}

    \vspace{.25em}

    {dannylongeuay@gmail.com --- https://www.ndsquared.net}
  \end{center}
}

\titleformat{\section}{\huge\bfseries}{\hspace{-.25in}}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[---]

\titlespacing{\subsection}{0em}{.25em}{0em}

\begin{document}

\title{Resume}
\author{Daniel Longeuay}

\maketitle

\section{Professional Summary}

Data-driven, detail-orientated, and insightful Site Reliability Engineer with proficiency in software
development, cloud infrastructure, automation, and container orchestration. Utilizes programming, CI/CD,
and infrastructure as code to build highly-available services. Measures service KPIs with rich telemetry
and monitoring. Exhibits leadership and collaboration skills through project design, implementation, 
deployment, and integration. Drives company-wide initiatives that provide value to multiple teams and customers.

\section{Technical Skills}

\subsection{CI/CD}

CodeFresh, Github Actions

\subsection{Cloud Providers}

AWS, GCP, DigitalOcean

\subsection{Configuration Management}

Ansible, Helm

\subsection{Containers/Orchestration}

Docker, Kubernetes, VMWare

\subsection{Infrastructure Provisioning}

Terraform, Pulumi

\subsection{Markup Languages}

HTML, {\LaTeX}, Markdown

\subsection{Monitoring}

DataDog, Grafana, InfluxDB, Prometheus, SNMP, Solarwinds, Splunk, Syslog

\subsection{Programming Languages}

Bash, Golang, Java, Javascript/Typescript, Python, Rust

\subsection{Web Development}

Flask, FastAPI, GraphQL, Nginx, NodeJS, REST, Svelte, TailwindCSS, VueJS

\section{Professional Experience}

Warner Bros. Discovery Staff Site Reliability Engineer Apr 2020 - Present

Design, develop, test, and deploy automation to reduce human labor.
Mentor junior team members on technology, development workflows, and mindset.
Develop and manage systems frameworks to deliver highly-available services.
Design, implement, and improve telemetry/analysis services.

iStreamPlanet Senior Site Reliability Engineer Jul 2020 - Apr 2022

Building highly available, geographically redundant services.
Developing tooling and automated pipelines for consistent delivery.
Reducing team silos with company-wide initiatives.
Building automation to treat systems operation as a software problem.
Enhancing monitoring to measure KPIs with infrastructure as code.

iStreamPlanet Network Engineer Oct 2019 - Jul 2020

Network management through CI/CD.
Building scalable monitoring and telemetry with infrastructure as code.
Developing hybrid cloud solutions for agile workflows.

NBCUniversal Senior Engineer, Network Automation May 2018 - Oct 2019

Automation design and implementation across Global Network Services.
Proactively ensure reliability and availability for NBCU's global applications.
Provide data analysis and metrics for LRP.
Automated configuration compliance and remediation on a global scale.
Built in-house tooling for network inventory analysis, reporting, and configuration backup.
Integrated internal APIs for monitoring dashboards.

NBCUniversal Network Engineer Jul 2015 - May 2018

Member of a team of professionals responsible for maintaining the health of the network, responding to 
incidents, troubleshooting, root cause analysis, allocation of IP addresses, network monitoring/alerts, 
and granting read/write access to network devices.
Team member responsibilities included, but not limited to automating standards and compliance checking, 
deploying configurations to the entire network portfolio, running reports/analysis for stakeholders, 
replacing end-of-life equipment, migrating services from one platform to another, and ensuring end-to-end 
support and quality of service.
Professional responsibilities include directly interfacing with stakeholders and hosting training sessions 
for various technologies and tools.

\section{Education}

California State San Bernardino
Bachelor of Arts in Mathematics

\end{document}
