%-------------------------
% Source : https://www.youtube.com/watch?v=VjsX4tznW40
% Author : Daniel Longeuay
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.25in]{geometry}
\usepackage[hidelinks]{hyperref}
\setcounter{secnumdepth}{0}
\pagestyle{empty}

\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries\theauthor}

    \vspace{.25em}

    {\href{mailto:dannylongeuay@gmail.com}{dannylongeuay@gmail.com} --- \href{https://ndsquared.net/}{ndsquared.net} --- \href{https://github.com/dannylongeuay}{github.com/dannylongeuay}}
  \end{center}
}

\titleformat{\section}{\huge\bfseries}{\hspace{-.25in}}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[---]

\titlespacing{\subsection}{.25em}{.25em}{0em}

\newcommand{\skill}[2]{\subsubsection{\hspace{.5em}#1\hfill\mdseries#2}\vspace{-.5em}}
\newcommand{\experienceHeading}[2]{\subsubsection{#1\hfill\mdseries{#2}\vspace{.75em}}}

\newcommand{\experienceItem}[2]{\item\small{\vspace{-.5em}\hspace{.25in}\bfseries#1$\Rightarrow$\mdseries#2}}
\newcommand{\experienceItemListStart}{\begin{itemize}}
\newcommand{\experienceItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\title{Resume}
\author{Daniel Longeuay}

\maketitle

\section{Professional Summary}

Data-driven, detail-orientated, and insightful Site Reliability Engineer with proficiency in software
development, cloud infrastructure, automation, and container orchestration. Utilizes programming, CI/CD,
and infrastructure as code to build highly-available services. Measures service KPIs with rich telemetry
and monitoring. Exhibits leadership and collaboration skills through project design, implementation, 
deployment, and integration. Drives company-wide initiatives that provide value to multiple teams and customers.

\section{Technical Skills}

  \skill{CI/CD}{CodeFresh, Github Actions}

  \skill{Cloud Providers}{AWS, GCP, DigitalOcean}

  \skill{Configuration Management}{Ansible, Helm}

  \skill{Containers/Orchestration}{Docker, Kubernetes, VMWare}

  \skill{Infrastructure Provisioning}{Terraform, Pulumi}

  \skill{Markup Languages}{HTML, {\LaTeX}, Markdown}

  \skill{Monitoring}{DataDog, Grafana, InfluxDB, Prometheus, Splunk}

  \skill{Programming Languages}{Bash, Golang, Java, Javascript/Typescript, Python}

  \skill{Web Frontend}{Nginx, NodeJS, Svelte, TailwindCSS, VueJS}

  \skill{Web Backend}{Flask, FastAPI, GraphQL, NodeJS}

\section{\vspace{.5em}Professional Experience}

  \experienceHeading{Warner Bros. Discovery Staff Site Reliability Engineer}{Apr 2022 - Present}

    \experienceItemListStart

      \experienceItem{Toil Elimination}{Design, develop, test, and deploy automation to reduce human labor.}

      \experienceItem{Hire and Develop the Best}{Mentor junior team members on technology, development workflows, and mindset.}

      \experienceItem{DevOps}{Develop and manage systems frameworks to deliver highly-available services.}

      \experienceItem{Monitoring}{Design, implement, and improve telemetry/analysis services.}

    \experienceItemListEnd

  \experienceHeading{iStreamPlanet Senior Site Reliability Engineer}{Jul 2020 - Apr 2022}

    \experienceItemListStart

      \experienceItem{Reliability}{Building highly available, geographically redundant services.}

      \experienceItem{Continuous Deployment}{Developing tooling and automated pipelines for consistent delivery.}

      \experienceItem{Cross-team}{Reducing team silos with company-wide initiatives.}

      \experienceItem{Automation as a Service}{Building automation to treat systems operation as a software problem.}

      \experienceItem{Monitoring}{Enhancing monitoring to measure KPIs with infrastructure as code.}

    \experienceItemListEnd

  \experienceHeading{iStreamPlanet Network Engineer}{Oct 2019 - Jul 2020}

    \experienceItemListStart

      \experienceItem{Network as a Service}{Network management through CI/CD.}

      \experienceItem{Monitoring}{Building scalable monitoring and telemetry with infrastructure as code.}

      \experienceItem{Cloud}{Developing hybrid cloud solutions for agile workflows.}

    \experienceItemListEnd

  \experienceHeading{NBCUniversal Senior Engineer, Network Automation}{May 2018 - Oct 2019}

    \experienceItemListStart

      \experienceItem{Automation}{Automation design and implementation across Global Network Services.}

      \experienceItem{High Availability}{Proactively ensure reliability and availability for NBCU's global applications.}

      \experienceItem{Data Analysis}{Provide data analysis and metrics for LRP.}

      \experienceItem{Security}{Automated configuration compliance and remediation on a global scale.}

      \experienceItem{Full Stack Development}{Built in-house tooling for network inventory analysis, reporting, and configuration backup.}

      \experienceItem{Monitoring}{Integrated internal APIs for monitoring dashboards.}

    \experienceItemListEnd

\section{Education}

  \experienceHeading{California State San Bernardino}{Bachelor of Arts in Mathematics}

\end{document}
